---
title: "RWorksheet#5_group(Lomibao,rabago and andigan)"
output: pdf_document
date: "2024-11-18"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
bow and load the necesssary packages
```{r}
library(kableExtra)
library("rvest")
library("polite")
library("dplyr")
library("stringr")

polite::use_manners(save_as = 'polite_scrape.R')
  
url <- "https://www.imdb.com/chart/toptv/?ref_=nv_tvv_250v"
webpage <- read_html(url)  
 session <- bow(url, 
                 user_agent = "Student education purpose")
 session
 page <- scrape(session)  
```
scraping the title 
```{r}
 title <- webpage%>%html_nodes('h3.ipc-title__text')%>%html_text()
 title <- title[2:26]
 title
```

```{r}
title_list <- as.data.frame(title[1:50])
colnames(title_list)<-"ranks"

```
spliting the data frame
```{r}
split_df <- strsplit(as.character(title_list$ranks),".",fixed = TRUE)
split_df<- data.frame(do.call(rbind,split_df))
split_df
```
renaming the columns
```{r}

split_df<-split_df[-c(3,4)]
colnames(split_df)<- c("Ranks","Titles")
split_df
```
scraping the star- rating and saving in the data frame
```{r}
ratings<- webpage %>% 
  html_nodes('span.ipc-rating-star--rating') %>%
  html_text()
ratings <- as.data.frame(ratings)
```
scraping the numbers of vote 
```{r}
number_votes <- webpage %>%
  html_nodes("span.ipc-rating-star--voteCount") %>%
  html_text()
number_votes <- as.data.frame(number_votes)
```
scraping the number of episode 
```{r}
num_ep <- webpage %>%
  html_nodes('span.sc-300a8231-7.eaXxft.cli-title-metadata-item:nth-of-type(2)')%>%
  html_text()
num_ep
```
cleanig the episode data.
```{r}
episode_counts <- str_extract(num_ep, "\\d+ eps")
number_episode <- str_remove(episode_counts, " eps")
number_episode <- as.data.frame(number_episode)
colnames(number_episode) <- "Episode"
number_episode
```
scraping the year release
```{r}
year <- webpage %>%
  html_nodes('span.sc-300a8231-7.eaXxft.cli-title-metadata-item') %>%html_text()
year
```
Exracting using the regex. 
```{r}
release_years <- str_extract(year, "\\d{4}")
release_years <- release_years[!is.na(release_years)]  # Remove NA values
release_years <- as.numeric(release_years)
relyear <- as.data.frame(release_years)
colnames(relyear) <-"Year"
relyear

```
creating csv file for every one of the data. 
```{r}
#title and ranks 
#rank_title <- data.frame(
 # rank_title = split_df)
#write.csv(rank_title,file = "title.csv")
#ranting 
#write.csv(rating,file = "star_rating.csv")
#vote count 
 #write.csv(number_votes,file = "vote_count.csv")
#year
 # write.csv(relyear = "year.csv")
#number of episode 
 #write.csv(number_episode = "number_episode.csv")

```
checking the length. 
```{r}
cat("Show Titles length: ", length(title), "\n")
cat("Show Ratings length: ", length(ratings), "\n")
cat("Number of Votes length: ", length(number_votes), "\n")
cat("Episode Counts length: ", length(number_episode), "\n")
cat("Release Years length: ", length(release_years), "\n")
```

```{r}

```
Combining them all to a data frame. 
```{r}
 # imdb_top_tv_shows <- data.frame(
 # Title = rank_title,
#  Rating = ratings,
#  Votes = number_votes,
 # Episode = episodes,
 # Release_Year = release_years,
  #stringsAsFactors = FALSE
 # )
#imdb_top_tv_shows

```

